\section{Size of Sets}

\subsection{Finite Sets}

\begin{definition}{Finite Set}{}
  A set $X$ is \textbf{finite} iff there exits an injection $f: X \to
  n$ for some natural number n.
\end{definition}

\begin{definition}{Number of elements}{}
  Suppose that $X$ is a finite set. Let $n$ be the least number s.t. there is
  an injection $f: X \to n$. Then $n$ is the \textbf{number of elements} in $X$,
  and we write $|X| = n$.
\end{definition}

\begin{theorem}{}{}
  Let $A$ be finite and $|A| = n$. If $f: A \to n$ is injective, then
  $f$ is surjective.
\end{theorem}

\begin{proof}
  If $A$ is empty, then $f$ is vacuously surjective. Assume $A$ is not empty.
  Suppose $f$ is not surjective, and let $k \in n \text{\ and\ } k
  \notin ran(f)$.
\end{proof}

\begin{corollary}{}{}
  If $A$ is finite and $|A| = n$, then there is a bijection $f: A \to n$.
\end{corollary}

\begin{theorem}{}{}
  Let $f: A \to A$ be injective and $A$ is finite. Then $f$ is surjective.
\end{theorem}

\begin{corollary}{Property of infinite set}{}
  Let $f: A \to A$ be injective and not surjective. Then $A$ is infinite.
\end{corollary}

\begin{theorem}{}{}
  Let $A$ and $B$ be finite sets. Then there is a bijection $f: A \to
  B$ iff $|A| = |B|$.
\end{theorem}

\begin{theorem}{}{}
  For all natural numbers $n$, $|n| = n$.
\end{theorem}

\begin{proof}{}{}

\end{proof}

\begin{corollary}{Pigeonhole Principle}{}
  Let $m$ and $n$ be natural numbers and $f: n \to m$. If $m < n$,
  then $f$ is not injective.
\end{corollary}

\begin{theorem}{}{}
  The set $\omega$ is an infinite set.
\end{theorem}

\begin{corollary}{}{}
  If $G: \omega \to A$ is injective, then $A$ is an infinite set.
\end{corollary}

\begin{lemma}{Dual version of Pigeonhole Principle}{}
  If $m < n$ and $f: m \to n$, then $f$ is not surjective.
\end{lemma}

\begin{theorem}{}{}
  If $N$ is finite and $f: N \to N$ is surjective, then $f$ is injective.
\end{theorem}

\begin{theorem}{}{}
  If $A$ is a finite set, then $\mathcal{P}(A)$ is finite.
\end{theorem}

\subsection{Countable Sets}

\begin{definition}{Countable Set}{}
  A set $X$ is countable iff there is injection $f :X \to \omega$.
\end{definition}

\begin{definition}{}{}
  A set $X$ is countably infinite iff it is countable and infinite.
\end{definition}

\begin{theorem}{}{}
  Let $A$ and $B$ are sets where $B$ is countable. If there is an
  injection $f: A \to B$, then $A$ is countable.
\end{theorem}

\begin{theorem}{}{}
  If $B$ is countable set and $A \subset B$, then $A$ is countable.
\end{theorem}
